Constraining the Interiors of Asteroids Through Close Encounters

### 2022-08-09 paper/appendices.tex
Finished orientation appendix

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.75\linewidth]{figs/orientation-unc}
  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data. First order parameters are shown in the left panel and second-order parameters in the right. Mean values are also shown as horizontal lines. Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
  \label{fig:orientation-unc}
\end{figure*}

The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$. This is expected due to the following argument. If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment. Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation. This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly. A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.

\subsection{Density uncertainty comparison}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figs/orientation-unc}
  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data. First order parameters are shown in the top panel and second-order parameters in the bottom. Mean values are also shown as vertical lines. Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
  \label{fig:orientation-unc}
\end{figure}

The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$. This is expected due to the following argument. If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment. Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation. This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly.

A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$, which will alter the density uncertainty discussed in the next section. However, this has little effect on the density distributions extracted by the finite element model from the two PPDs shown in the figure. The average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the distribution of density and density uncertainty extracted.

@@
